\chapter*{Acknowledgements}
\markboth{Acknowledgements}{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}
% put your text here
First of all, I would like to thank my advisors Mark Pauly and Andrea Tagliasacchi.

I am grateful to Mark for hiring me to work on hand tracking. This topic was in demand at the start of my PhD and it is even more so at the time of my graduation. Thanks to Mark, my first project was extremely well chosen. I was not starting from scratch, but working in a team of experienced researchers. The techniques that I learned fueled my entire PhD. Another crucial point that I want to thank for is freedom that I was given. I came to doctoral school with a goal to become an independent researcher which is impossible without some freedom to choose work directions and make mistakes.

I would like to express my deepest gratitude to Andrea Tagliasacchi. I was inspired by his energy, devotion to research and even more so by his long term vision and revolutionary ideas. Also I am grateful for his patience, and technical and moral support at difficult stages of my research. Andrea guided me through stagnation and dead ends to accepted papers. It motivated me a lot to see that he personally cares about success and well-being of his students and is ready to make big efforts to help. I would like to express my hope that our collaboration will go on for decades.

I am thankful to Sofien Bouaziz for supervising my Master Thesis and co-supervising my first PhD projects. Sofien was always there for me to give technical advice, answer questions or simply cheer me up. I owe Sofien my lucky choice career, since I joined the lab to continue working with him.

I would like to extend my gratitude to my collaborators Mario Botsch, Andrew Fitzgibbon, Edoardo Remelli and Matthias Schröder. The presence of Matthias brightened the deadline for our first project. The company of Edoardo and the possibility to discuss the technical details of the project on the daily basis made the last year my PhD more fun.

I would like to thank Andrew Fitzgibbon for supervising my internship at Microsoft Research. It was a privilege to have weekly discussions and look at the way he approaches research problems. I am also grateful to Federica Bogo and Tom Cashman for their help and advice.

I am thankful to Luciano Sbaiz and Wei Li for mentoring my internship at Google Research. It was an intense learning experience and their guidance and support made a big difference.

I am thankful to my thesis committee for finding the time in their busy schedule to review my thesis and conduct the oral exam: Mario Botsch, Mark Pauly, Mathieu Salzmann, Andrea Tagliasacchi and Jonathan Taylor.

I am grateful to Merlin Nimier-David for his huge help in creating the template hand model. I also thank Timur Bagautdinov, Pierre Baqué, Jan Bednarik, Anna Biletta, Filippo Candia, Pei-I Chen, Alexis Dewaele, Giacomo Garegnani, Fabrice Guibert, Tomas Joveniaux, Isinsu Katircioglu, Mina Konakovic, Andrii Maksai, Hannah Pauly, Edoardo Remelli, Madeleine Robert, Stefano Savare and Matthieu Sauvé for participation in creating online hand calibration dataset.

I would like to thank my LGG lab mates for sharing this experience with me: Sofien Bouaziz, Duygu Ceylan, Minh Dang, Mario Deuss, Alexandru-Eugen Ichim, Mina Konakovic, Stefan Lienhard, Peng Song, Yuliy Schwartzburg, Andrea Tagliasacchi, Ziqi Wang. I am grateful to Madeleine Robert for all the help. In general I thank my fellow PhD students in EDIC for their company, especially the ones who came to board games nights and my collocation neighbors Arseniy Zaostrovnykh and Dmitrii Ustiugov.

Finally, my biggest thanks go to my parents and my life partner Andrii for their love and support. Thank you, Andrii, sharing with me every moment and making me happy.

My research has been supported by the funding from FNS project 200021\_153567.

%\bigskip
 
%\noindent\textit{Lausanne, 12 Mars 2011}
%\hfill D.~K.
